Return Oriented Programming

### 2023-02-10 presentation.tex
changes

\section{Introduction}
\subsection{Basic information}
\begin{frame}
    \frametitle{What is Return Oriented Programming?}
    \begin{itemize}
    \item A type attack that exploits buffer overruns
    \item Published by Hovav Shacham in 2007
    \item Arised as a technique to counter security mechanisms (NX)
    \item Big binary $\rightarrow$ ROP is turing complete
    \item Many authors refer to ret-to-libc/library as ROP, according to the founder of this technique it has to be differentiated and ROP describes chaining of small code segments
    \end{itemize}
\end{frame}

@@

>>>>

\section{Introduction}
\subsection{Basic information}
\begin{frame}
    \frametitle{What is Return Oriented Programming?}
    \begin{itemize}
    \item A type of attack that exploits buffer overruns
    \item Arised as a technique to counter security mechanisms (NX)
    \item Research by Hovav Shacham et al in 2007 - "When good instructions go bad: generalizing return-oriented programming to RISC"
    \item Blackhat conference 2008, Hovav Shacham - "Return-oriented Programming:
    Exploitation without Code Injection" \url{https://hovav.net/ucsd/talks/blackhat08.html}
    \item Paper published by Ryan Roemer, Erik Buchanan, Hovav Shacham and Stefan Savage in 2012 - "Return-Oriented Programming: Systems, Languages, and Applications" 
    \item Big binary $\rightarrow$ ROP is turing complete
    \item Many authors refer to ret-to-libc/library as ROP, according to the founder of this technique it has to be differentiated and ROP describes chaining of small code segments
    \end{itemize}
\end{frame}

@@

\section{How to find suitable Gadgets?}
\begin{frame}
    \begin{itemize}
    \item Search gadgets
    \end{itemize}
    \bltCommand{ropcommand.sh}{Dumping Gadgets}{dumpgadget}
    \begin{itemize}
        \item 34011 Gadgets - 716,056 kB binary
        \item Most of them are not very useful but the sheer size makes it likely we have suitable candidates, using regular expressions we can find suitable candidates fast
        \item Example 1: pop edx $\rightarrow$ \regex{\^{}.* pop edx ; .*ret}
        \item Example 2: int 0x80 $\rightarrow$ \regex{\^{}.* int 0x80}
        \item Example 3: xor eax, eax $\rightarrow$ \regex{\^{}.* xor eax, eax ; .*ret}
    \end{itemize}
\end{frame}
